### 2024-06-05 getting-started.qmd
20240605 - figure captions

```{r}
# Prepare Data
rushing_attempts <- nfl_pbp %>% 
  dplyr::filter(
    season_type == "REG") %>% 
    filter(
      rush == 1,
      rush_attempt == 1,
      qb_scramble == 0,
      qb_dropback == 0,
      !is.na(rushing_yards))

@@

```{r}
# Subset Data
rb_seasonal <- player_seasonal_offense %>% 
  filter(position_group == "RB")

# Create Plot
ggplot2::ggplot(
  data = rb_seasonal,
  ggplot2::aes(
    x = age,
    y = rushing_epa)) +
  ggplot2::geom_point() +
  ggplot2::geom_smooth() +
  ggplot2::labs(
    x = "Rushing Back Age (years)",
    y = "Rushing EPA/season",
    title = "2023 NFL Rushing EPA per Season by Player Age"
  ) +
  ggplot2::theme_classic()
```

>>>>

```{r}
#| label: fig-rushYPCperSeasonByAge
#| fig-cap: "2023 NFL Rushing Yards Per Carry per Season by Player Age"

# Prepare Data
rushing_attempts <- nfl_pbp %>% 
  dplyr::filter(
    season_type == "REG") %>% 
    filter(
      rush == 1,
      rush_attempt == 1,
      qb_scramble == 0,
      qb_dropback == 0,
      !is.na(rushing_yards))

@@

```{r}
#| label: fig-rushEPAperSeasonByAge
#| fig-cap: "2023 NFL Rushing Expected Points Added (EPA) per Season by Player Age"

# Subset Data
rb_seasonal <- player_seasonal_offense %>% 
  filter(position_group == "RB")

# Create Plot
ggplot2::ggplot(
  data = rb_seasonal,
  ggplot2::aes(
    x = age,
    y = rushing_epa)) +
  ggplot2::geom_point() +
  ggplot2::geom_smooth() +
  ggplot2::labs(
    x = "Rushing Back Age (years)",
    y = "Rushing EPA/season",
    title = "2023 NFL Rushing Expected Points Added (EPA) per Season by Player Age"
  ) +
  ggplot2::theme_classic()
```
